---
title: "A7"
output:
  html_document:
    code_folding: hide
css: styles.css
---


```{r init, include=FALSE, echo=FALSE}
## load API keys
source("./scripts/process_data.R")
## you may also load necessary libraries and set various options here
library(dplyr)
library(data.table)
library(ggplot2)
library(knitr)
knitr::opts_chunk$set(error=TRUE)
                           # continue compiling on error

writeLines("td, th { padding : 6px } th { background-color : brown ; color : white; border : 1px solid white; } td { color : brown ; border : 1px solid brown } body { color:white; background-color:black; font-family: Arial, Helvetica, sans-serif; }", con = "styles.css")
```

##Timing Tests

For our timing tests, we chose to compare the speed of two methods of reading in CSV files: _fread_ and _read.csv_. All four of our group members use Macbooks (OS X operating systems), so our results may not be as varied as a group of testers on different operating systems.

For reference, by _fread_ we mean **fread("{sample.data}.csv")**, and by _read.csv_ we mean **read("{sample.data}.csv")**.

In order to test our computers processing time, we compared the benchmark timings for reading in data as well as filtering datasets. We all have macbooks with relatively similar memory and cpus. If you're interested in the functions we used to test these timings you can click the code button to the right.

```{r}

testRead <- function() {
  m <- summary(microbenchmark(read.csv("data/UFOCoords.csv"), fread("data/UFOCoords.csv")))
  return(m)
}
testFilter <- function() {
  df <- fread("data/UFOCoords.csv")
  m <- summary(microbenchmark(df[match("CANADA", df$Country, nomatch=0),], filter(df, Country == "CANADA"), df %>% filter(Country == "CANADA")))
  return(m)
}
```
```{r , echo=FALSE}
df <- fread("data/table_results.csv")
knitr::kable(df, format = "html")
```



##UFO Sightings

The first things we were curious about when it came to the UFO sightings data was where they were sighted. To get a better sense of this, we created a map showing each UFO sighting:


```{r , echo=FALSE, warning=FALSE}

ufo_map

```

*(The data for Hawaii was excluded from the map in the interest of visibility.)*


As you can see, the UFO sightings seem to be most highly-concentrated in the Northeastern region of the USA, and are predictably scarce in areas with small human populations.



Next, we chose to plot the various reported UFO shapes in a bar graph:

```{r , echo=FALSE, warning=FALSE}

ufo_shapes

```


The most common shapes were _light_, _circle_, and _triangle_, which is likely due to observers only seeing the UFO for a small amount of time and being unable to discern a more complex shape, such as _teardrop_, _chevron_, etc.. However, there were still a surprisingly high amount of sightings that were reported to be of these complex-shaped UFOs.




