---
title: "A7"
output:
  html_document: default
css: styles.css
---


```{r init, include=FALSE, echo=FALSE}
## load API keys
source("./scripts/process_data.R")
## you may also load necessary libraries and set various options here
library(dplyr)
library(data.table)
library(ggplot2)
library(knitr)
knitr::opts_chunk$set(error=TRUE)
                           # continue compiling on error
```

##Timing Tests

For our timing tests, we chose to compare the speed of two methods of reading in CSV files: _fread_ and _read.csv_. All four of our group members use Macbooks (OS X operating systems), so our results may not be as varied as a group of testers on different operating systems.

For reference, by _fread_ we mean **fread("{sample.data}.csv")**, and by _read.csv_ we mean **read("{sample.data}.csv")**.



##UFO Sightings

The first things we were curious about when it came to the UFO sightings data was where they were sighted. To get a better sense of this, we created a map showing each UFO sighting:


```{r , echo=FALSE, warning=FALSE}

ufo_map

```

*(The data for Hawaii was excluded from the map in the interest of visibility.)*


```{r , echo=FALSE, warning=FALSE}

ufo_shapes

```



